% ACKNOWLEDGEMENT
\newpage

\begingroup
\renewcommand{\cleardoublepage}{}
\clearpage
\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
\endgroup

\begin{spacing}{2.0}
First and foremost, I would like to express my sincere thanks to Professor John H. Weare, who contributed greatly to my current self.
His guidance teaches me to look at problems from multiple dimensions, and gives me freedom to explore things, both academically and
non-academically. All these allow me to compile bits and pieces of seemingly unrelated knowledge into a distinct package that
I today cherish.

For my current standing in the academia, I would like to thank these three people: Professor George C. Schatz of Northwestern Universit
and Dr. Nicolas Winter, for introducing me to the world of theoretical chemistry and my fabulous experience in Chicago, and Dr. Eric J. 
Bylaska at PNNL for introducing me to the wonderful Python programming language, as well as for tiredlessly helping me with using NWChem.

This thesis would not complete without the help from Professor Gabor Cs\'{a}nyi of the University of Cambridge for his immense help
    during the early stage of my work on Gaussian Process Regression (GPR), as well as Professor Jonathan Weare of the University of Chicago for 
    his advices on free energy computations in general, as well as the Eigenvector Method for Umbrella Sampling (EMUS) algorithm. 
I would like to also thank Professor Cecilia Clementi of Rice University,
    and Professor Frank No\'{e} of the Free University of Berlin for a close collaboration and numerous theoretical exchanges on Markov State Model (MSM). 
    They are also extremely helpful and answered all my questions without hesitating. It was my great pleasure working with them. 
I also would like to thank and acknowledge the committee members, Professor Clifford Kubiak, Professor Katja Lindenberg, Professor
Francesco Paesani, and Professor Ruth Williams for their time and guidance.

To all Weare Group members that I knew: Dr. Ying Chen and Duo Song, it has been a pleasure for me to get to know and work with both of you.
I wish both of you all the best for your future endeavors. 

    I would not become a person I am today without the supports from the following people:
        Sumaetee Tangwancharoen (Por),
        Pisrut Phummirat (Todd), and
        Kullachate Muangnapoh (Oath),
            my past roommates. I appreciate all the time we spent together, no matter happy or sad, and also the fact that all of you
            are the first refuge of strength in my darkest days. You guys are truly my great friends! Thank you for everything,
            and let us keep in touch!
        Kantapon Kaewtip (Jom),
            for many insightful conversations.
        Thada Udomprapasup (Kim),
            for being a good-natured persona that inspires me to be devoted to the causes.
        Teerapong Pirojsirikul (Tee), and
        Wiroj Nanthasetpong (Wave),
            for being my nice and honest friends who I can always turn to every time.
        Watcharapong Hongjamrassilp (WiN),
            for your neverending curiosity and your positive energy bursts, and
        Pichaya Lertvilai (Tonmai),
            for a place to stay to write this thesis, and all your intellectual capacity.
    Moreover, I would like to also extend my thanks to all my other friends who might not be named here who contributed bits and pieces
    at some point of time in my life. No matter how small they are, they all constitute and influence my current self. Thank you
    for being an integral part of my life!

Also, I would like to thank my parents for their neverending supports, especially during the toughest moments of the study. With the 
completion of this dissertation and the thesis defense, I vow to make you proud!

Last but not least, I would like to thank UCSD and the surrounding communities. Living in California
has shaped a new, different way of thinking in me, and seeing all the new innovations in such a cradle is an honor to me. These
truly inspire me to keep innovating and be different.
\end{spacing}
